---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# saros: Semi-Automatic Reporting of Ordinary Surveys

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Codecov test coverage](https://codecov.io/gh/NIFU-NO/saros/branch/main/graph/badge.svg)](https://app.codecov.io/gh/NIFU-NO/saros?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/saros)](https://CRAN.R-project.org/package=SAROS)
[![CRAN release](https://www.r-pkg.org/badges/version-ago/saros)](https://CRAN.R-project.org/package=SAROS)
[![CRAN total downloads](https://cranlogs.r-pkg.org/badges/grand-total/saros)](https://CRAN.R-project.org/package=SAROS)
[![R-CMD-check](https://github.com/NIFU-NO/saros/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/NIFU-NO/saros/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Introduction
saros (Semi-Automatic Reporting of Ordinary Surveys) is an R package designed to handle repeating surveys within the same project that occur annually or biannually. It aims to automate the process of summarizing and reporting on survey data, helping researchers save time and maintain consistency across survey iterations. Specifically, SAROS produces highly customizable figures, text, analyses and reports for a batch of possible dependent-independent relations of possible interest.


### Connection to the Astronomical concept of Saros
The term "saros" also refers to a cyclical phenomenon in astronomy known as the Saros cycle, which represents a period of approximately 18 years, 11 days, and 8 hours. After one Saros, the Sun, Earth, and Moon return to approximately the same relative positions, leading to a similar eclipse.

* Cyclical occurrences: Both versions of SAROS refer to cyclical events that recur at regular intervals. In the case of the R package, it relates to surveys that are repeated annually or biannually, while in astronomy, it refers to the recurring pattern of eclipses.

* Consistency: The SAROS R package aims to maintain consistency in reporting and analysis across survey iterations, just as the astronomical Saros cycle represents a predictable pattern in the occurrence of solar and lunar eclipses.

* Time-saving: The SAROS R package is designed to automate and streamline the process of summarizing and reporting on survey data, saving researchers time and effort. Similarly, the Saros cycle is a useful tool for astronomers to predict and plan for future eclipses, making it easier to study these events without having to make complex calculations each time.



## Installation

The development version from [GitHub](https://github.com/) with:

``` r
install.packages("pak")
pak::pak("sda030/saros")
```


## Initialize a social science project

```{r example}
### CURRENTLY NOT WORKING. MOVE TO ANOTHER PACKAGE?
#> saros::initialize(folder = getwd())
```


```{r example2}
# Define temporary folder for storing the elements
library(saros)
output_index_qmd <-
  draft_report(chapter_overview = ex_survey_ch_overview, 
             data = ex_survey1, 
             mesos_var = "f_uni",
             path = tempdir()
             )
quarto::quarto_render(output_index_qmd, as_job = FALSE)
if(interactive()) {
  browseURL(output_index_qmd)
  browseURL(fs::path(tempdir(), "index.html"))
}
```

    

```{r example3}
# Define temporary folder for storing the elements
library(saros)
output_index_qmd <-
  draft_report(chapter_overview = 
                 dplyr::mutate(ex_survey_ch_overview, 
                               indep = ifelse(.data$indep == "x1_sex",
                                              "x1_sex,x2_human", 
                                              .data$indep)),
              data = ex_survey1[ex_survey1$f_uni %in% c("Uni of A", "Uni of B"), ], 
               title = "My first report - ",
               mesos_var = "f_uni",
               label_separator = " - ",
               name_separator = "_",
              groupby = c("chapter", ".element_name", ".variable_label_prefix"),
               index_filename = "main_index.qmd",
               data_label = "percentage_bare",
               always_show_bi_for_by = "x1_sex",
               totals = TRUE,
               hide_label_if_prop_below = .05, 
               hide_test_if_n_below = 10,
               mesos_first = TRUE,
               colour_palette = nifutheme::nifu_cols(),
               digits = 0,
               data_label_decimal_symbol = ",",
             path = tempdir())
system.time(
  for(file in output_index_qmd) {
    quarto::quarto_render(file, as_job = TRUE)
  }
  )
if(interactive()) {
  browseURL(fs::path(tempdir(), "Uni of C", "Uni of C_main_index.html"))
}
```


## Documentation
Please see the [documentation](https://NIFU-NO.github.io/saros/).

## Licence: saros is not free to use.
In contrast to many R packages, this package is NOT free to use for any Norwegian institution or person unless explicit written permission has been given by the author, or NIFU. For anyone else in the world, it is free to use for commercial and non-commercial purposes. However, reproduction is not allowed.

## Code of Conduct

Please note that the saros project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
