---
title: "Preparing the data for a Saros-report drafting - for data cleaners"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Preparing the data for a Saros-report drafting - for data cleaners}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Data preparation for Saros
-   Ensure that all variables have variable labels (see `{labelled}`-package or `{sjLabelled}`).
    -   Item sets (batteries/cosntructs) sharing the same main question should be meticulously ensured to have the exact same prefix to the label - a slight difference in whitespace will result in them being placed on different graphs.
-   Categorical variables must be of type factor or ordered, not the temporary `labelled` class.
    - Distinguishing between factor-class (unordered) and ordered class matters in Saros - for colour palettes.
    - You do not want to create dummy variables.
-   Open text variables must be stored as character. These will be visualized/displayed appropriately. Remember that you have the responsibility to consider anonymity!
-   Continuous/integer variables are so far not really supported.
-   Most other things can be adjusted in the draft_report() argument (see [For project managers](for_project_managers.Rmd) for more info on configurations).

```{r setup}
library(sarosverse)


```
